Convective penetration probably parameterizes convective overshoot

### 2021-07-23 manuscript/ms.tex
auto-generate latex table
cleans up all the figs and data

This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 20 days on 1024 cores for a total of $\sim$500,000 cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.

@@

In Fig.~\ref{fig:AE_time_figure}, we plot in black the time evolution of $\delp$ and $f$ in Case I simulations with $\mS = 10^3$, $\mR = 400$, and $\mP_D = [1,2,4]$.
We overplot the evolution of simulations which use this accelerated evolution (AE) procedure using orange and green lines.
Time units on the x-axis are normalized in terms of the total simulation run time in order to more thoroughly demonstrate the evolutionary differences between standard timestepping and AE.
However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/8$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
AE simulations with orange lines start with PZ heights which are much larger than the final height, while green line solution start with initial PZ heights which are smaller than the expected height.
Regardless of our choice of initial condition, we find that this AE procedure quickly evolves our simulations to within a few percent of the final value.
After converging to within a few percent of the proper penetration zone height, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration before jumping back towards it in the next iteration.
If the PZ height continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the changes of $\delp$ have diminished.

@@

\colhead{Type} 	& \colhead{$\mP$}	& \colhead{$\mS$}	& \colhead{$\mR$}	& \colhead{$nz \times (nx \times ny)$}	&	\colhead{$t_{\rm{sim}}$}	&	\colhead{$(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$}	& \colhead{$f$}	& \colhead{$\xi$}	& \colhead{$\angles{u}$}

@@

D	& 1	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 12347	& ($0.078, 0.112, 0.136$)	& 0.81	& 0.70	& 0.61 \\
D	& 2	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 22593	& ($0.191, 0.220, 0.242$)	& 0.75	& 0.62	& 0.62 \\
D	& 4	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 57170	& ($0.434, 0.461, 0.483$)	& 0.67	& 0.58	& 0.62 \\

@@

D		& 0.1,  & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 4561 	& ($0.017, 0.042, 0.069$)	&  0.83	&  0.77	& 0.59 \\
D		& 0.3,  & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 4681 	& ($0.030, 0.064, 0.092$)	&  0.81	&  0.80	& 0.62 \\
D		& 1,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 3000 	& ($0.082, 0.116, 0.140$)	&  0.80	&  0.69	& 0.62 \\
D		& 2,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 5000 	& ($0.199, 0.228, 0.252$)	&  0.75	&  0.60	& 0.64 \\
D		& 4,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 5000 	& ($0.452, 0.480, 0.505$)	&  0.67	&  0.55	& 0.62 \\
D		& 6,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 6000 	& ($0.620, 0.647, 0.667$)	&  0.64	&  0.53	& 0.60 \\
D		& 8,    & $10^3$    & $4 \times 10^2$   & 512$\times$128$^2$	& 4357 	& ($0.731, 0.757, 0.778$)	&  0.64	&  0.48	& 0.59 \\
D		& 10,   & $10^3$    & $4 \times 10^2$   & 512$\times$128$^2$	& 4226 	& ($0.857, 0.884, 0.903$)	&  0.63	&  0.45	& 0.59 \\
D   	& 4		& $10^3$			& 25				& 256$\times$16$^2$ 	& 3000	& (0.321, 0.379, 0.437)	& 0.77	& 0.27	& 0.34 \\
D   	& 4		& $10^3$			& 50				& 256$\times$32$^2$ 	& 3000	& (0.398, 0.442, 0.487)	& 0.73	& 0.36	& 0.42 \\
D   	& 4		& $10^3$			& $1 \times 10^2$	& 256$\times$32$^2$ 	& 3000	& (0.469, 0.503, 0.534)	& 0.67	& 0.46	& 0.48 \\
D   	& 4		& $10^3$			& $2 \times 10^2$	& 256$\times$64$^2$ 	& 3000	& (0.485, 0.515, 0.542)	& 0.65	& 0.55	& 0.55 \\
D   	& 4		& $10^3$			& $8 \times 10^2$	& 256$\times$128$^2$	& 3000	& (0.407, 0.434, 0.455)	& 0.69	& 0.57	& 0.68 \\
D   	& 4		& $10^3$			& $1.6 \times 10^3$	& 256$\times$128$^2$	& 3000	& (0.366, 0.397, 0.419)	& 0.71	& 0.57	& 0.72 \\
D   	& 4		& $10^3$			& $3.2 \times 10^3$	& 256$^3$				& 2469	& (0.313, 0.350, 0.372)	& 0.73	& 0.60	& 0.75 \\
D   	& 4		& $10^3$			& $6.4 \times 10^3$	& 384$^3$				& 414 	& (0.277, 0.314, 0.335)	& 0.74	& 0.62	& 0.76 \\
D/SF	& 4		& $10^3$			& 50				& 256$\times$16$^2$ 	& 5000	& (0.435, 0.477, 0.516)	& 0.68	& 0.42	& 0.50 \\
D/SF	& 4		& $10^3$			& $1 \times 10^2$	& 256$\times$32$^2$ 	& 5000	& (0.482, 0.516, 0.547)	& 0.64	& 0.54	& 0.57 \\
D/SF	& 4		& $10^3$			& $2 \times 10^2$	& 256$\times$32$^2$ 	& 5000	& (0.490, 0.520, 0.547)	& 0.63	& 0.59	& 0.64 \\
D/SF	& 4		& $10^3$			& $4 \times 10^2$	& 256$\times$64$^2$ 	& 8000	& (0.474, 0.502, 0.531)	& 0.65	& 0.59	& 0.69 \\
D/SF	& 4		& $10^3$			& $8 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.410, 0.437, 0.461)	& 0.68	& 0.59	& 0.73 \\
D/SF	& 4		& $10^3$			& $1.6 \times 10^3$	& 256$\times$128$^2$	& 5710	& (0.368, 0.400, 0.426)	& 0.70	& 0.59	& 0.76 \\
D/SF	& 4		& $10^3$			& $3.2 \times 10^3$	& 256$^3$				& 2933	& (0.315, 0.352, 0.381)	& 0.73	& 0.59	& 0.77 \\
D		& 4		& $10^2$			& $4 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.377, 0.505, 0.581)	& 0.65	& 0.53	& 0.62 \\
D		& 4		& $3\times 10^2$	& $4 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.420, 0.477, 0.514)	& 0.66	& 0.55	& 0.62 \\
D		& 4		& $3\times 10^3$	& $4 \times 10^2$	& 256$\times$128$^2$	& 1170	& (0.455, 0.472, 0.487)	& 0.66	& 0.58	& 0.62 \\
L		& 0.01	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1139	& (0.017, 0.030, 0.052)	& 0.87	& 0.79	& 0.45 \\
L		& 0.03	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 929 	& (0.021, 0.045, 0.070)	& 0.86	& 0.79	& 0.45 \\
L		& 0.1	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1142	& (0.084, 0.076, 0.102)	& 0.85	& 0.72	& 0.45 \\
L		& 0.3	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1109	& (0.077, 0.130, 0.158)	& 0.82	& 0.66	& 0.45 \\
L		& 1		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 3000	& (0.182, 0.225, 0.251)	& 0.79	& 0.60	& 0.44 \\
L		& 2		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 3000	& (0.278, 0.315, 0.340)	& 0.76	& 0.57	& 0.44 \\
L		& 4		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 5000	& (0.396, 0.427, 0.449)	& 0.73	& 0.53	& 0.43 \\
L		& 8		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 5000	& (0.519, 0.545, 0.562)	& 0.72	& 0.48	& 0.42 \\
L		& 16	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 8000	& (0.687, 0.709, 0.723)	& 0.70	& 0.44	& 0.42 \\

>>>>

This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 24 days on 1024 cores for a total of $\sim$600,000 cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.

@@

In Fig.~\ref{fig:AE_time_figure}, we plot in black the time evolution of $\delp$ and $f$ in Case I simulations with $\mS = 10^3$, $\mR = 400$, and $\mP_D = [1,2,4]$.
We overplot the evolution of simulations which use this accelerated evolution (AE) procedure using orange and green lines.
Time units on the x-axis are normalized in terms of the total simulation run time in order to more thoroughly demonstrate the evolutionary differences between standard timestepping and AE.
However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/10$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
AE simulations with orange lines start with PZ heights which are much larger than the final height, while green line solution start with initial PZ heights which are smaller than the expected height.
Regardless of our choice of initial condition, we find that this AE procedure quickly evolves our simulations to within a few percent of the final value.
After converging to within a few percent of the proper penetration zone height, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration before jumping back towards it in the next iteration.
If the PZ height continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the changes of $\delp$ have diminished.

@@

\colhead{Type} 	& \colhead{$\mP$}	& \colhead{$\mS$}	& \colhead{$\mR$}	& \colhead{$nx \times ny \times nz$}	&	\colhead{$t_{\rm{sim}}$}	&	\colhead{$(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$}	& \colhead{$f$}	& \colhead{$\xi$}	& \colhead{$\angles{u}$}

@@

D & $1.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 12347$ & (0.078, 0.112, 0.136) &  0.810 &  0.682 &  0.618 \\
D & $ 2.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 32057$ & (0.200, 0.230, 0.254) &  0.749 &  0.601 &  0.639 \\
D & $ 4.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 66557$ & (0.445, 0.472, 0.496) &  0.668 &  0.562 &  0.619 \\

@@

D & $ 4.0$ & $ 10^{2}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.377, 0.505, 0.581) &  0.654 &  0.526 &  0.617 \\
D & $ 4.0$ & $3.0 \cdot 10^{2}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.420, 0.477, 0.514) &  0.663 &  0.551 &  0.618 \\
D & $ 10^{-1}$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 4561 $ & (0.017, 0.042, 0.069) &  0.831 &  0.769 &  0.588 \\
D & $ 3.0 \cdot 10^{-1}$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 4681 $ & (0.030, 0.064, 0.092) &  0.814 &  0.804 &  0.620 \\
D & $1.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 3000 $ & (0.082, 0.116, 0.140) &  0.804 &  0.690 &  0.624 \\
D & $ 2.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.199, 0.228, 0.252) &  0.750 &  0.597 &  0.638 \\
D & $ 4.0$ & $ 10^{3}$ & $ 2.5 \cdot 10^{1}$ &  16x16x256   & $ 3000 $ & (0.321, 0.379, 0.437) &  0.772 &  0.274 &  0.343 \\
D & $ 4.0$ & $ 10^{3}$ & $ 5.0 \cdot 10^{1}$ &  32x32x256   & $ 3000 $ & (0.398, 0.442, 0.487) &  0.732 &  0.358 &  0.423 \\
D & $ 4.0$ & $ 10^{3}$ & $ 10^{2}$ &  32x32x256   & $ 3000 $ & (0.469, 0.503, 0.534) &  0.672 &  0.464 &  0.484 \\
D & $ 4.0$ & $ 10^{3}$ & $ 2.0 \cdot 10^{2}$ &  64x64x256   & $ 3000 $ & (0.485, 0.515, 0.542) &  0.648 &  0.546 &  0.548 \\
D & $ 4.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.452, 0.480, 0.505) &  0.667 &  0.553 &  0.617 \\
D & $ 4.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 3000 $ & (0.407, 0.434, 0.455) &  0.689 &  0.566 &  0.678 \\
D & $ 4.0$ & $ 10^{3}$ & $ 1.6 \cdot 10^{3}$ &  128x128x256 & $ 3000 $ & (0.366, 0.397, 0.419) &  0.709 &  0.574 &  0.720 \\
D & $ 4.0$ & $ 10^{3}$ & $ 3.2 \cdot 10^{3}$ &  256x256x256 & $ 3235 $ & (0.321, 0.358, 0.381) &  0.723 &  0.605 &  0.746 \\
D & $ 4.0$ & $ 10^{3}$ & $ 6.4 \cdot 10^{3}$ &  384x384x384 & $ 414  $ & (0.277, 0.315, 0.335) &  0.744 &  0.605 &  0.757 \\
D & $ 6.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 6000 $ & (0.620, 0.647, 0.667) &  0.635 &  0.532 &  0.597 \\
D & $ 8.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  128x128x512 & $ 4357 $ & (0.732, 0.759, 0.779) &  0.640 &  0.481 &  0.592 \\
D & $ 10^{1}$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  128x128x512 & $ 4226 $ & (0.858, 0.885, 0.904) &  0.630 &  0.453 &  0.587 \\
D & $ 4.0$ & $3.0 \cdot 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x512   & $ 1170 $ & (0.437, 0.454, 0.469) &  0.672 &  0.581 &  0.619 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 5.0 \cdot 10^{1}$ &  32x32x256   & $ 5000 $ & (0.435, 0.477, 0.516) &  0.680 &  0.418 &  0.505 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 10^{2}$ &  32x32x256   & $ 5000 $ & (0.482, 0.516, 0.547) &  0.638 &  0.543 &  0.573 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 2.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.490, 0.520, 0.547) &  0.634 &  0.589 &  0.640 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 8000 $ & (0.474, 0.502, 0.531) &  0.651 &  0.588 &  0.693 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 5000 $ & (0.410, 0.437, 0.461) &  0.683 &  0.587 &  0.732 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 1.6 \cdot 10^{3}$ &  128x128x256 & $ 5710 $ & (0.368, 0.400, 0.426) &  0.703 &  0.590 &  0.758 \\
D/SF & $ 4.0$ & $ 10^{3}$ & $ 3.2 \cdot 10^{3}$ &  256x256x256 & $ 3917 $ & (0.320, 0.357, 0.388) &  0.725 &  0.595 &  0.772 \\
L & $ 10^{-2}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 1139 $ & (0.017, 0.030, 0.051) &  0.873 &  0.783 &  0.445 \\
L & $ 3.0 \cdot 10^{-2}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 929  $ & (0.020, 0.044, 0.070) &  0.863 &  0.782 &  0.448 \\
L & $ 10^{-1}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 1142 $ & (0.081, 0.076, 0.102) &  0.848 &  0.725 &  0.450 \\
L & $ 3.0 \cdot 10^{-1}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 1109 $ & (0.076, 0.129, 0.157) &  0.825 &  0.655 &  0.451 \\
L & $1.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 3000 $ & (0.182, 0.225, 0.251) &  0.787 &  0.599 &  0.442 \\
L & $ 2.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 3000 $ & (0.278, 0.315, 0.340) &  0.759 &  0.570 &  0.436 \\
L & $ 4.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 10000$ & (0.399, 0.431, 0.455) &  0.737 &  0.518 &  0.428 \\
L & $ 8.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 5000 $ & (0.519, 0.545, 0.562) &  0.718 &  0.484 &  0.421 \\
L & $ 1.6 \cdot 10^{1}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 8000 $ & (0.687, 0.709, 0.723) &  0.700 &  0.442 &  0.417 \\
